---
output: github_document
---

# mlr3verse

Package website: [release](https://mlr3.mlr-org.com/) | [dev](https://mlr3.mlr-org.com/dev)

Meta-package for installing/updating [mlr3* packages](https://github.com/mlr-org/mlr3/wiki/Extension-Packages).

[![CRAN status](https://www.r-pkg.org/badges/version/mlr3verse)](https://cran.r-project.org/package=mlr3verse)
[![Build Status](https://img.shields.io/travis/mlr-org/mlr3verse/master?label=Linux&logo=travis&style=flat-square)](https://travis-ci.org/mlr-org/mlr3verse)
[![codecov](https://codecov.io/gh/mlr-org/mlr3verse/branch/master/graph/badge.svg)](https://codecov.io/gh/mlr-org/mlr3verse)
[![StackOverflow](https://img.shields.io/badge/stackoverflow-mlr3-orange.svg)](https://stackoverflow.com/questions/tagged/mlr3)
[![Dependencies](https://tinyverse.netlify.com/badge/mlr3verse)](https://cran.r-project.org/package=mlr3verse)

## Overview

The _mlr3verse_ is a set of packages that work in harmony because they share common data representations and API design (similar to the [tidyverse](https://tidyverse.tidyverse.org/) but with differing principles). 
The **mlr3verse** package is designed to make it easy to install and load core packages
from the **mlr3verse** in a single command.

## Installation

``` r
remotes::install_github("mlr-org/mlr3verse")
```

## CRAN Packages

```{r, echo=FALSE, message=FALSE}
library(magrittr)
library(mlr3verse)
out = mlr3misc::map(mlr3verse_packages(cran_only = TRUE, 
                                       include_self = FALSE), packageDescription)
Title = mlr3misc::map_chr(out, function(x) x$Title)
Name = mlr3misc::map_chr(out, function(x) x$Package)
URL =  mlr3misc::map_chr(out, function(x) strsplit(x$URL[1], ",")[[1]][1])

data.frame(Name, Title, URL) %>% 
  knitr::kable()
```

## Github Packages

```{r, echo = FALSE, message=FALSE}
gh_pkgs = setdiff(mlr3verse:::deps_all(), mlr3verse:::deps_cran())
out = mlr3misc::map(setdiff(mlr3verse:::deps_all(), mlr3verse:::deps_cran()), packageDescription)
Title = mlr3misc::map_chr(out, function(x) x$Title)
Name = mlr3misc::map_chr(out, function(x) x$Package)
URL =  mlr3misc::map_chr(out, function(x) strsplit(x$URL[1], ",")[[1]][1])

data.frame(Name, Title, URL) %>% 
  knitr::kable()
```

You can check that all _mlr3verse_ packages are up-to-date with
`mlr3verse_update()`

## Graphical overview

<a href="https://raw.githubusercontent.com/mlr-org/mlr3/master/man/figures/mlr3verse.svg?sanitize=true"><img src="https://raw.githubusercontent.com/mlr-org/mlr3/master/man/figures/mlr3verse.svg?sanitize=true" /></a>

## Core packages

If you call `library("mlr3verse")` the following core packages will be loaded:

- mlr3
- mlr3pipelines
- mlr3learners
- paradox
- mlr3tuning
