---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

Package website: [release](https://mlr3verse.mlr-org.com/) | [dev](https://mlr3verse.mlr-org.com/dev)

Meta-package for installing/loading core [mlr3 packages](https://github.com/mlr-org/mlr3/wiki/Extension-Packages).

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mlr3verse

<!-- badges: start -->
[![Build Status](https://img.shields.io/travis/mlr-org/mlr3verse/master?label=Linux&logo=travis&style=flat-square)](https://travis-ci.org/mlr-org/mlr3verse)
[![R CMD Check via {tic}](https://img.shields.io/github/workflow/status/mlr-org/mlr3verse/R%20CMD%20Check%20via%20%7Btic%7D?logo=github&label=R%20CMD%20Check%20via%20{tic}&style=flat-square)](https://github.com/mlr-org/mlr3verse/actions)
[![cran checks](https://cranchecks.info/badges/worst/mlr3verse)](https://cran.r-project.org/web/checks/check_results_mlr3verse.html)
[![CRAN Status Badge](https://www.r-pkg.org/badges/version-ago/mlr3verse)](https://cran.r-project.org/package=mlr3verse)
[![codecov](https://codecov.io/gh/mlr-org/mlr3verse/branch/master/graph/badge.svg)](https://codecov.io/gh/mlr-org/mlr3verse)
[![StackOverflow](https://img.shields.io/badge/stackoverflow-mlr3-orange.svg)](https://stackoverflow.com/questions/tagged/mlr3)
<!-- badges: end -->

## Overview

This package is intended to simplify both installation and loading of packages from the mlr3 ecosystem.

## Installation

``` r
# From CRAN:
install.packages("mlr3verse")

# From Github:
remotes::install_github("mlr-org/mlr3verse")
```

## Batteries included

The following packages are attached by this meta package:

| Name          | Title                                                        | URL                                 |
| :------------ | :----------------------------------------------------------- | :---------------------------------- |
| mlr3          | Machine Learning in R - Next Generation                      | <https://mlr3.mlr-org.com>          |
| mlr3filters   | Filter Based Feature Selection for ‘mlr3’                    | <https://mlr3filters.mlr-org.com>   |
| mlr3learners  | Recommended Learners for ‘mlr3’                              | <https://mlr3learners.mlr-org.com>  |
| mlr3pipelines | Preprocessing Operators and Pipelines for ‘mlr3’             | <https://mlr3pipelines.mlr-org.com> |
| mlr3tuning    | Tuning for ‘mlr3’                                            | <https://mlr3tuning.mlr-org.com>    |
| mlr3viz       | Visualizations for ‘mlr3’                                    | <https://mlr3viz.mlr-org.com>       |
| paradox       | Define and Work with Parameter Spaces for Complex Algorithms | <https://paradox.mlr-org.com>       |


By loading the `mlr3verse` package, you are all set to deal with most regression and classification tasks:

```{r}
library("mlr3verse")
```

If you want to get more detailed information about the loaded packages, you can call `mlr3verse_info()`:

```{r}
mlr3verse_info()
```

More extension packages are available on CRAN/GitHub, and may be included in this meta package in the future.

<a href="https://raw.githubusercontent.com/mlr-org/mlr3/master/man/figures/mlr3verse.svg?sanitize=true"><img src="https://raw.githubusercontent.com/mlr-org/mlr3/master/man/figures/mlr3verse.svg?sanitize=true" /></a>
